Effectful Semantics for Substructural SSA

### 2023-11-04 pldi24/paper.tex
Tap
Taps

@@

\TODO{distributive category}

\TODO{Elgot category}

@@

\TODO{premonoidal/effectful categories}

\TODO{Elgot structure}

\TODO{relevant/affine/intuitionistic subcategories}

@@

\section{Basic Models}

@@

\section{Separation Logic}

@@

\section{Weak Memory}

@@

@@

\TODO{\cite{promonad}}

\TODO{\cite{linear-state-usage}}

>>>>

\subsection{Isotope Models}

\TODO{intro text}

\TODO{define premonoidal category}

\TODO{pull Elgot structure up here?}

@@

\TODO{relate separation logic trick to \cite{promonad}, \cite{linear-state-usage}}

\begin{definition}[Distributive category] 
  A \textbf{distributive category} is a premonoidal category with coproducts equipped with a natural family of central isomorphisms \(\delta_{A, B, C}: (A + B) \otimes C \simeq A \otimes C + B \otimes C\).
\end{definition}

\begin{definition}[Elgot category] 
  An \textbf{Elgot category} is a category \(\mc{C}\) with coproducts equipped with an operator \(\cdot^\dagger: \mc{C}(A, B + A) \to \mc{C}(A, B)\) satisfying the following properties:
  \begin{itemize}
    \item \textbf{Fixpoint:} ...
    \item \textbf{Naturality:} ...
    \item \textbf{Codiagonal:} ...
    \item \textbf{Uniformity:} ...
  \end{itemize}
  A monad \(\mb{T}\) on \(\mc{C}\) such that its Kleisli cateogry \(\mc{C}_{\mb{T}}\) is Elgot is called an \textbf{Elgot monad}.
\end{definition}

\TODO{distributivity of monads}

\TODO{result: if a monad is Elgot, the state/reader/writer transformers yield Elgot monads}

\TODO{example of Elgot monads: traces}

\subsection{Denotational Semantics}

\TODO{refactor below}

@@

@@

\subsection{Optimizations}

\TODO{this...}

\section{Concrete Models}

\subsection{Basic Models}

@@

\TODO{already done above?}

\subsection{Separation Logic}

@@

\subsection{Weak Memory}

@@

\TODO{remove? time + space...}

@@
